Methods and Results

### 2022-10-04 ms.Rmd
Adding new plot with lnCVR and lnVR

    ## Overall intercept only models. Note that, for lnCVR, 3 effect sizes are based on non-ratio data so are not defined and are excluded.
    model1_lnCVR <- rma.mv(logCVR ~ 1, V = v_logCVR, 
                       random = list(~1|study, ~1|obs, ~1|species), dfs = "contain", test = "t", 
                       method = "REML", data = data)
    robust_model1_lnCVR <- robust(model1_lnCVR, cluster = data$study, vcov = "CR2")

    model1_lnVR <- rma.mv(logVR ~ 1, V = v_logVR, 
                       random = list(~1|study, ~1|obs, ~1|species), dfs = "contain", test = "t", 
                       method = "REML", data = data)
    robust_model1_lnVR <- robust(model1_lnVR, cluster = data$study, vcov = "CR2")

    orchard_plot(model1_lnCVR, group = "study", data = data, 
                 xlab = "log Coefficient of Variation (lnCVR)") + 
    labs(x = "Overall Mean Estimate")
  ###############
      # Final tables
  ################
  # Tables
                n1.7 <- sperm_data %>% group_by(SCR.SCI) %>% summarise(n = n(), nstdy = length(unique(study)), moderator = unique(SCR.SCI))
      n1.7[3,c(2,3)] <- t(c(dim(data)[1], with(data, length(unique(study)))))
  robust_model1.7_PI <- pred_interval(robust_model1.7_reparam, c(4.404, 1.88, 2.49)) # Ignore PIs not used and not correct
  robust_model1.7_PI <- cbind(robust_model1.7_PI, n1.7)

>>>>

# Exclude 4 studies that fail test. 3 effects are not defined in anycase
    data_cvr <- data %>% filter(geary_test == "pass")

    ## Overall intercept only models. Note that, for lnCVR, 3 effect sizes are based on non-ratio data so are not defined and are excluded.
    model1_lnCVR <- rma.mv(logCVR ~ 1, V = v_logCVR, 
                       random = list(~1|study, 
                                     ~1|obs, 
                                     ~1|species), 
                       dfs = "contain", test = "t", 
                       method = "REML", data = data_cvr)
    robust_model1_lnCVR <- robust(model1_lnCVR, cluster = data_cvr$study, vcov = "CR2")

    model1_lnVR <- rma.mv(logVR ~ 1, V = v_logVR, 
                       random = list(~1|study, 
                                     ~1|obs, 
                                     ~1|species), 
                       dfs = "contain", test = "t", 
                       method = "REML", data = data_cvr)
    robust_model1_lnVR <- robust(model1_lnVR, cluster = data_cvr$study, vcov = "CR2")

   p1 <-  orchard_plot(model1_lnCVR, group = "study", data = data_cvr, 
                 xlab = "log Coefficient of Variation Ratio (lnCVR)") + 
          labs(x = "Overall Mean Estimate") +
          theme(axis.text.y = element_blank(),
                legend.position = 'none')
   p2 <-  orchard_plot(model1_lnVR, group = "study", data = data_cvr, 
                 xlab = "log Variance Ratio (lnVR)") + 
          labs(x = element_blank()) +
          theme(axis.text.y = element_blank())

   (p1 | p2) + plot_annotation(tag_levels = "A", tag_suffix = ")")
